Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-04-11 Text/Review-and-suggestions-Prof.-Abraao-R1.tex
Changes added in Rmd file

In this article, we have provided a practical and theoretical answer to the following physical question: How to detect texturelessness in SAR images, assuming that the SAR intensity follows the $\mathcal{G}^0_I$ distribution.
Solving this problem is not easy, considering that the texturelessness in the parametric space of $\mathcal{G}^0_I$ means the infinity value, which is neither analitically tractable nor practically provable.
To this end, we have proposed three novel hypothesis tests, one from the Shannon entropy and two others from the variation coefficient variants.

>>>>

In this article, we have provided a practical and theoretical answer to the following physical question: How to detect texturelessness in SAR images, assuming that the SAR intensity follows the $\mathcal{G}^0_I$ distribution.
Solving this problem is not easy, considering that the texturelessness in the parametric space of $\mathcal{G}^0_I$ means the infinity value, which is neither analitically tractable nor practically provable.
To this end, we proposed three novel hypothesis tests, one from the Shannon entropy and two others from the variation coefficient variants.
The performance of our proposals was evaluated using a Monte Carlo study. The results showed that they were conservative in estimating the probability of a type I error (false alarm rate) and the test power (probability of detection), which increases with sample size.
An application to two recent SAR images was performed. The results showed that the $\text{CV}_{\text{MnAD}}$ and Shannon entropy-based tests were more robust than the CV-based tests. In addition, the CV-based tests were able to recognize both images without texture and those where the type of texture changes.
